### 2014-09-22 fundamentals/impl.tex
added a toolkit section, closes #22

\subsection{Toolkit}
% library of tools
% contributions to the toolkit
% place for metrics

The toolkit is a place for developers and users to contribute common-use tools 
for calculating metrics, managing process physics, and handling data.

This was implemented by liberal use of namespaces and is populated with an
introductory suite of useful tools, including helper classes for managing
facility deployment, minimum cost facility deployment decision making, and for
enrichment-related calculations.

>>>>

\subsection{Toolkit}

In addition to the core functionality of the \Cyclus kernel, which is focused on
the minimal set of capabilities needed to implement an agent-based simulation
with dynamic resource exchange, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an activly developed module module of \Cyclus, with a primary forward-looking
focus on supporting interesting \textit{in situ} (i.e., in simulation) and
\textit{ex situ} (i.e., post-processing) metric analysis tools.

\subsubsection{Simulation Tools}

A series of utility classes are provided to support demand-constrained agent
(e.g. facility) deployment. Symbolic function representations of linear,
expontential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mixin classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have some nameplate
capacity to produce a given commdity, and the \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
$\phi_i$, and costs $c_i$.

\begin{equation}
\begin{aligned}
 \min & \sum_{i=1}^{N}c_i y_i \\
 s.t. & \sum_{i=1}^{N}\phi_i y_i \ge \Phi \\
      & n_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer} 
\end{aligned}
\end{equation}

\subsubsection{Nuclear Engineering Tools}

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First the \Class{MatQuery} module
provides a basic querying API, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an API for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material given provided feed, product, and tails
assays.
